---
title: "Introduction to Uncertainty"
author: "Callum Clark"
date: "04/02/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Install packages

```{r}
if (!require("pacman")) install.packages("pacman")

pacman::p_load(tidyverse)
pacman::p_load(readxl)
library(magrittr)

```

## Estimating height
```{r}

samples <- c()

mx <- mean(samples)
stdev <- sd(samples)
hist(samples)
abline(v = mx, col = "blue", lwd = 2)
abline(v = mx+stdev, col = "red", lwd = 2)
abline(v = mx-stdev, col = "red", lwd = 2)
```


## R combining uncertainties exercise

```{r}
dir <- "C:/Users/callum.clark/Desktop/R uncertainty seminar"


data <- readxl::read_excel(paste0(dir,"/Defra_recycling_data_exercise2.xlsx"), sheet = "Black_bag_waste") 

```

What is the 95% sampling error for food waste, garden waste, other organic and paper respectively?

```{r}

data$se[data$primary_level_category == "Food waste"] <- 0.43

data$se[data$primary_level_category == "Garden waste"] <- 0.00998

data$se[data$primary_level_category == "Other organic"] <- 0.06

data$se[data$primary_level_category == "Paper"] <- 0.75
```


## Expert judgement

```{r}

london_latitude <- 55.4
london_homicides_2019 <- 149 
uk_pop_2019 <- 66.9
UK_waste_generated <- 223
coronavirus_cases <- 

guesses <- list(alex = c(1,1,1,0,0), callum = c(0,0,0,0,0))
confidences <- list(alex = c(0.9,0.6,0.7,0.5,0.5), callum = c(0.9,0.9,1,0.9,0.9))

calculate_brier_score <- function(guess,confidence) {
    stopifnot(length(guess) == length(confidence))
    brier_score = 1/length(guess) * purrr::map2(guess,confidence, function(x,y)  (y - x)^2) %>%
	        purrr::reduce(`+`)
			
	return(brier_score)
	
}

calculate_brier_scores <- function(guesses,confidences) {

	brier_scores = purrr::map2(guesses, confidences, function(x,y) calculate_brier_score(x,y))
	
	return(brier_scores)
}

brier_scores <- calculate_brier_scores(guesses, confidences)
barplot(unlist(brier_scores))
```
```{r}
calculate_brier_score(guesses[["callum"]],confidences[["callum"]])
guesses[1]
```


## Monte-carlo exercise 

Exercise 1: generate inputs

```{r}

generate_impacts <- function(data) {
              data %>% 
               dplyr::mutate(generated_percentage_of_waste = rnorm(n(), mean = `percentage_of_total_household_residual_waste`, sd = `se`),
			             policy_A_impact = runif(n(), min = `Policy_A_tonnage_reduction_lower`, max =`Policy_A_tonnage_reduction_upper`),
			             policy_B_impact = runif(n(), min = `Policy_B_tonnage_reduction_lower`, max =`Policy_B_tonnage_reduction_upper`),  
                         policy_C_impact = runif(n(), min = `Policy_C_tonnage_reduction_lower`, max =`Policy_C_tonnage_reduction_upper`),
						 A_impact_tonnes = policy_A_impact * generated_percentage_of_waste * uk_total_household_residual_waste,
						 B_impact_tonnes = policy_B_impact * generated_percentage_of_waste * uk_total_household_residual_waste,
						 C_impact_tonnes = policy_C_impact * generated_percentage_of_waste * uk_total_household_residual_waste) %>%   
			   dplyr::select(primary_level_category, A_impact_tonnes, B_impact_tonnes, C_impact_tonnes)
}
  

run_monte_carlo <- function(n, data) {
    lst <- 1:n
    dfs <- purrr::map(lst, function(x) generate_impacts(data))
	
	return(dfs)
}

runs <- run_monte_carlo(10000, data)
food_waste_runs <- purrr::map(runs, function(x) dplyr::filter(x, primary_level_category == "Food waste") %>% dplyr::select(A_impact_tonnes, B_impact_tonnes, C_impact_tonnes))
food_waste <- dplyr::bind_rows(food_waste_runs) 
rownames(food_waste) <- 1:nrow(food_waste)


```

Exercise 2: 

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.


## Structured group expert judgment


